---
title: "Reverse Engineering Project"
author: William Beltran, Stephanie Quinn, Sarah Siock and Jamille Whitlow!!!
date: 2022/10/8
output:
  html_document:
    theme: cerulean
    highlight: pygments
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction 

In this notebook, we are reverse engineering the story, "In North Carolina, Black Voters' Mail-In Ballots Much More Likely to Be Rejected Than Those From Any Other Races" (https://www.propublica.org/article/in-north-carolina-black-voters-mail-in-ballots-much-more-likely-to-be-rejected-than-those-from-any-other-race)

## Load libraries

Loading required libraries for this analysis.

```{r echo=FALSE, message=FALSE}
library(tidyverse)
library(janitor)
library(lubridate)
library(dplyr)
```

## Load and Cleaning Data

In this section, describe the source of the data, write a basic data dictionary for data you are working with, and discuss any caveats or issues you discovered working with this data. 

```{r}
# Load required data

nc_absentee_data <- read_csv("data folder/absentee_20181106.csv")

nc_absentee_data

glimpse(nc_absentee_data)

problems(nc_absentee_data)
# Path to data should be loaded from folder "data" i.e. read_csv("data/name_of_data.csv")

# Clean required data and prepare for analysis if needed. 


```
```{r}
nc_absentee_data <- read_csv("data folder/absentee_20181106.csv", guess_max=2111797)
```
```{r}
nc_absentee_data
```

## Sentences to Engineer
In this notebook, we are reverse engineering five sentences from the story.

### Sentence 1

* **Sentence text**: [Vance County rejected more than a quarter of the 110 mail-in ballots returned by Black voters. In contrast, only five ballots out of 102 submitted by white voters were rejected.]
* **Analysis summary**: [Write up two to three sentences describing the results of your analysis.  Were you able to confirm the finding? If not, why not?]
We filtered for Black voters in Vance County. Then, to find the total number of Black voters in Vance County who requested mail ballots, we filtered for "MAIL" as the ballot request type. We got 110 voters.

To find the number of Black voters' mail-in ballots that were rejected, we filtered out accepted ballots using !=. We got 29 rejected mail-in ballots. To find the proportion of Black voters' ballots that were rejected, we divided 29 by 110. That shows a 26.4% rejection rate, which fits the authors' statement that more than a quarter of Black voters' mail-in ballots were rejected.

We repeated the same methodology for white voters in Vance County. 
```{r}
# Put code to reverse engineer sentence here
nc_absentee_data %>% 
  filter(county_desc == "VANCE", race == "BLACK or AFRICAN AMERICAN") %>% 
  filter(ballot_req_type == "MAIL"& !is.na(ballot_rtn_dt))
```
To figure out how many Black voters' mail-in ballots were rejected, we filtered out accepted and one-stop ballots. In North Carolina, one-stop early voting enables voters to cast a ballot early in person. Since these votes are cast in person, we filtered them out.

```{r}

nc_absentee_data %>% 
  filter(county_desc == "VANCE" & race == "BLACK or AFRICAN AMERICAN" ) %>% 
 filter(ballot_req_type == "MAIL"& !is.na(ballot_rtn_dt)) %>% 
  filter(ballot_rtn_status != "ACCEPTED") %>% 
  filter(ballot_req_type != "ONE-STOP")
```
We used n_distinct to try to get closer to ProPublica's number of rejected ballots. Either way, we found that just over a quarter of Black voters' mail-in ballots were rejected in Vance County.
```{r}
nc_absentee_data %>% 
  filter(county_desc == "VANCE" & race == "BLACK or AFRICAN AMERICAN" ) %>% 
  filter(ballot_rtn_status != "ACCEPTED") %>% 
  filter(ballot_req_type != "ONE-STOP") %>% 
  group_by(voter_reg_num) %>% 
  summarize(distinct_reg_numbers = n_distinct(voter_reg_num))
```

WHITE VOTERS
We filtered for Vance County and white voters, and for voters who requested mail-in ballots.
```{r}
nc_absentee_data %>% 
  filter(county_desc == "VANCE" & race == "WHITE") %>% 
  filter(ballot_req_type == "MAIL"& !is.na(ballot_rtn_dt))
```


To figure out how many white voters' mail-in ballots were rejected, we filtered out accepted and one-stop ballots.
```{r}
nc_absentee_data %>% 
  filter(county_desc == "VANCE" & race == "WHITE" ) %>% 
  filter(ballot_req_type == "MAIL"& !is.na(ballot_rtn_dt)) %>% 
  filter(ballot_rtn_status != "ACCEPTED") %>% 
  group_by(voter_reg_num) %>% 
  summarise(count = n())
```


# Display results of code below this codeblock

=======

### Sentence 2

* **Sentence text**: In 73 out of 92 counties where Black voters returned at least one mail-in ballot, those ballots were rejected at a higher rate than those returned by white voters. 
* **Analysis summary**: We first found 92 counties where black voters returned at least one mail-in ballot. In order to find the rate of rejection in each county we wrote code to find the total number of ballots and number of rejected for Black voter and white voters. For both Black voters and white voters we merged the tables with the rejected and the total votes. We then used transform to divide the number of rejected ballots by the total and created a new column using summarize. In counties where the percent of black rejected ballots divided by percent of white rejected ballots was more than one, Black voters ballots were rejected at a higher rate than white voters' ballots. We then counted the number of times this occurred which was 70. 

=======

```{r}
# Counties where Black voters turned in at least one mail-in ballot
nc_absentee_data %>% 
  filter(race == "BLACK or AFRICAN AMERICAN") %>% filter(ballot_req_type == "MAIL"& !is.na(ballot_rtn_dt)) %>% 
  group_by(county_desc) %>% 
  summarize(count = n()) %>% 
  arrange(count)
```

```{r}
# rejected mail-in ballots for Black voters in each county
nc_absentee_data %>% 
  filter(race == "BLACK or AFRICAN AMERICAN") %>% filter(ballot_req_type == "MAIL"& !is.na(ballot_rtn_dt)) %>% 
  filter(ballot_rtn_status != "ACCEPTED") %>% 
  filter(ballot_req_type != "ONE-STOP") %>% 
  group_by(county_desc) %>% 
  summarize(count = n())

#total mail in ballots for black voters in each county
nc_absentee_data %>% filter(race == "BLACK or AFRICAN AMERICAN" & ballot_req_type == "MAIL" & !is.na(ballot_rtn_dt)) %>% group_by(county_desc) %>%
  summarize(black_mail_in_votes = n())


```
```{r}
# naming new column
black_voters_mail_in <- nc_absentee_data %>% filter(race == "BLACK or AFRICAN AMERICAN" & ballot_req_type == "MAIL" & !is.na(ballot_rtn_dt)) %>% group_by(county_desc) %>% summarize(black_mail_in_votes = n())
```

```{r}
# naming other new column
black_voters_rejected <- nc_absentee_data %>% 
  filter(race == "BLACK or AFRICAN AMERICAN" & ballot_req_type == "MAIL"& !is.na(ballot_rtn_dt)) %>% filter(ballot_rtn_status != "ACCEPTED") %>% 
  filter(ballot_req_type != "ONE-STOP") %>% 
  group_by(county_desc) %>% 
  summarize(black_rejected_mail_in = n())

```
```{r}
# joining total and rejected Black mail-in ballot info
# calculated percent Black mail-in ballots rejected
black_voters <- black_voters_mail_in %>% 
  left_join(black_voters_rejected, by="county_desc") %>% 
  transform(black_percent_rejected = black_rejected_mail_in / black_mail_in_votes)

black_voters
```
```{r}
# Counties where white voters cast at least one mail-in ballot
white_voters_mail_in <- nc_absentee_data %>% 
  filter(race == "WHITE" & ballot_req_type == "MAIL"& !is.na(ballot_rtn_dt)) %>% 
  group_by(county_desc) %>% 
  summarize(white_mail_in_votes = n())

white_voters_mail_in
```

```{r}
# Number of white mail-in ballots rejected per county
white_voters_rejected <- nc_absentee_data %>% 
  filter(race == "WHITE" & ballot_req_type == "MAIL"& !is.na(ballot_rtn_dt)) %>% 
  filter(ballot_rtn_status != "ACCEPTED") %>% 
  filter(ballot_req_type != "ONE-STOP") %>% 
  group_by(county_desc) %>% 
  summarize(white_rejected_mail_in = n())

white_voters_rejected
```

```{r}
# joining total and rejected white mail-in ballot info
# calculating percent white mail-in ballots rejected
white_voters <- white_voters_mail_in %>% 
  left_join(white_voters_rejected, by="county_desc") %>% 
  transform(white_percent_rejected = white_rejected_mail_in / white_mail_in_votes)
```

```{r}
# joining data for white and black voters
# created a column comparing black and white percent rejected
# arranged in descending order of rejection rate to county where black mail-in ballots were rejected more often than white mail-in ballots
combined_voters <- black_voters %>% 
  left_join(white_voters, by="county_desc") %>% 
  transform(total_rejection_rate = black_percent_rejected / white_percent_rejected) %>% 
  arrange(desc(total_rejection_rate))

combined_voters
```

### Sentence 3

* **Sentence text**: Guilford County, the third-most populous county in North Carolina, rejected the largest number of mail-in ballots by Black voters statewide: 177. The rejection rate for Black voters, at 16.5%, was three times as high as the rejection rate for white voters, 5.5%, putting the county largely in line with the rest of the state.
* **Analysis summary**: First, we confirmed that Guilford rejected the most mail-in ballots by writing code to rank the counties in order of Black voters rejected ballots. We then wrote code to get the number of Black mail in ballots and then the number rejected. We then divided the number of Black mail in by the number rejected. We repeated to the same process for white voters. We got a 16.5% rejection rate for Black voters and a 5.5% rejection rate for white voters. 

```{r}
# Put code to reverse engineer sentence here

# Display results of code below this codeblock

#Rejected ballots in each county to confirm Guilford was the highest
nc_absentee_data %>% filter(race == "BLACK or AFRICAN AMERICAN") %>% filter(ballot_req_type == "MAIL"& !is.na(ballot_rtn_dt)) %>%
filter(ballot_rtn_status != "ACCEPTED") %>% 
    group_by(county_desc) %>% 
     summarize(count = n()) %>% 
    arrange(desc(count))

#number of Black mail in in Guilford 
  nc_absentee_data %>% filter(county_desc == "GUILFORD", race == "BLACK or AFRICAN AMERICAN") %>%
  filter(ballot_req_type == "MAIL" & !is.na(ballot_rtn_dt)) %>%
  summarize(count = n())

#number of Black mail in rejected in Guilford
  nc_absentee_data %>%  filter(county_desc == "GUILFORD", race == "BLACK or AFRICAN AMERICAN") %>% 
  filter(ballot_req_type == "MAIL"& !is.na(ballot_rtn_dt)) %>%
  filter(ballot_rtn_status != "ACCEPTED") %>% 
  summarize(count = n())

  
  #White mail in ballots
  nc_absentee_data %>%  filter(county_desc == "GUILFORD", race == "WHITE") %>% 
  filter(ballot_req_type == "MAIL" & !is.na(ballot_rtn_dt)) %>%
  summarize(count = n())

  #number of white mail in ballots rejected
  nc_absentee_data %>%  filter(county_desc == "GUILFORD", race == "WHITE") %>% 
  filter(ballot_req_type == "MAIL" & !is.na(ballot_rtn_dt)) %>%
  filter(ballot_rtn_status != "ACCEPTED") %>% 
  summarize(count = n())
 
 
```

### Sentence 4

* **Sentence text**: Black voters weren’t the only affected minority in North Carolina in 2018. Across all minority groups, voters were nearly twice as likely to have their mail-in ballots rejected compared with white voters. But the disparity is particularly stark for Black voters, whose ballots formed 14% of the about 104,000 cast by mail in 2018. Black voters’ mail-in ballots saw a 14% rejection rate, more than twice the 6.3% rate of all voters’ mail-in ballots statewide and the highest of all racial groups.
* **Analysis summary**: First we use n distinct to determine the number of minority groups in the data. Going through the data we found seven total races, five of them being minority races.Then we filtered for minority groups for mail in and removed NAs. Next we added a filter for ballots not accepted. We grouped by race and then counted the number of rejected ballots for each group. Next, we found the total mail in for all minority groups. Then we joined total mail in and total rejected for the minority groups. We repeated the same process for white voters. 

Then we found total mail in for the state and then total black voters mail in, from there we could verify that Black voters mail in ballots were 14% of all mail in ballots. We then found the rejected ballots for the whole state. 

```{r}
nc_absentee_data %>%  summarize(minority_groups=n_distinct(race))

#minority total mail in
minority_total_mailin <- nc_absentee_data %>%
  filter(race == "BLACK or AFRICAN AMERICAN" | race == "TWO or MORE RACES" | race == "OTHER" | race == "INDIAN AMERICAN or ALASKA NATIVE" | race == "ASIAN") %>%
  filter(ballot_req_type == "MAIL" & !is.na(ballot_rtn_dt)) %>%
  group_by(race) %>%
  summarize(count = n())

#minority rejected
minority_rejected_mailin <- nc_absentee_data %>%
  filter(race == "BLACK or AFRICAN AMERICAN" | race == "TWO or MORE RACES" | race == "OTHER" | race == "INDIAN AMERICAN or ALASKA NATIVE" | race == "ASIAN") %>%
  filter(ballot_req_type == "MAIL" & !is.na(ballot_rtn_dt)) %>%
  filter(ballot_rtn_status != "ACCEPTED") %>%
  group_by(race) %>%
  summarize(count = n())

#percent rejection rate for each minority
rejection_rate <- minority_rejected_mailin %>%
  left_join(minority_total_mailin, by="race")
rejection_rate %>%
  rename(rejected = count.x, total = count.y)
#rejected numbers 
#Percent rejected mail-in by race
#Asian: 7.1%
#Black: 13.6%
#Indian: 7.9%
#Other: 7.6%
#Two or more races: 7.5%

#white rejected and white mail in
white_rejected_mailin <- nc_absentee_data %>%
  filter(race == "WHITE") %>%
  filter(ballot_req_type == "MAIL" & !is.na(ballot_rtn_dt)) %>%
  filter(ballot_rtn_status != "ACCEPTED") %>%
  summarize(count = n())

white_total_mailin <- nc_absentee_data %>%
  filter(race == "WHITE") %>%
  filter(ballot_req_type == "MAIL" & !is.na(ballot_rtn_dt)) %>%
  summarize(count = n())


#total percent of voter that were Black or African American
nc_absentee_data %>%
  filter(ballot_req_type == "MAIL" & !is.na(ballot_rtn_dt)) %>%
  summarize(count = n())

nc_absentee_data %>%
  filter(race == "BLACK or AFRICAN AMERICAN") %>%
  filter(ballot_req_type == "MAIL" & !is.na(ballot_rtn_dt)) %>%
  summarize(count = n())

#statewide mail in
statewide_mailin <- nc_absentee_data %>% filter(ballot_req_type == "MAIL" & !is.na(ballot_rtn_dt))

#rejection for mail in state wide
statewide_mailin_rejected <- nc_absentee_data %>% filter(ballot_req_type == "MAIL" & !is.na(ballot_rtn_dt)) %>%  filter(ballot_rtn_status != "ACCEPTED")


```

### Sentence 5

* **Sentence text**:Rockingham County, which is 33% Black by population, had a 37% rejection rate for Black ballots and a 10% rejection rate for white ballots in 2018.
* **Analysis summary**: First we figured out the number of mail in ballots for African American voters in Rockingham county. Then we found the number of rejected black voters mail in in Rokcingham using filter and summarize. We divided these numbers be each other to get the percent rejected. We repeated the same process for white voters. 

```{r}
 #Rockingham total mail
Rockingham_total_mail <- nc_absentee_data %>% 
  filter(county_desc == "ROCKINGHAM", race == "BLACK or AFRICAN AMERICAN") %>% 
  filter(ballot_req_type == "MAIL"& !is.na(ballot_rtn_dt)) %>% 
   summarize(count = n())

#Rockingham rejected
Rockingham_black_rejected <- nc_absentee_data %>% filter(county_desc == "ROCKINGHAM" & race == "BLACK or AFRICAN AMERICAN" ) %>% 
 filter(ballot_req_type == "MAIL"& !is.na(ballot_rtn_dt)) %>% 
  filter(ballot_rtn_status != "ACCEPTED") %>% 
  filter(ballot_req_type != "ONE-STOP") %>% 
  summarize(count = n())

#Total rejection
Rockingham_black_rejected/Rockingham_total_mail*100

#Rockingham white total mail 
rock_total_white <- nc_absentee_data %>%
  filter(county_desc == 'ROCKINGHAM', race == 'WHITE', ballot_req_type == 'MAIL' & !is.na(ballot_rtn_dt))%>% 
   summarize(count = n())

#Rockingham rejected white total mail 
rock_rejected_white <- nc_absentee_data %>% filter(county_desc == 'ROCKINGHAM', race == 'WHITE', ballot_req_type == 'MAIL' & !is.na(ballot_rtn_dt)) %>% 
  filter(ballot_rtn_status != 'ACCEPTED')%>% 
   summarize(count = n())

#total rejection
rock_rejected_white/rock_total_white*100

```


## 

-30-